Teaching Dossier

### 2020-02-27 CUT/teaching-philosophy.tex
Student evaluations

\section{Evaluation of Teaching}
I find feedback on my teaching to be tremendously valuable. It is the easiest way for me to identify potential avenues for improvement, while at the same time motivating me by highlighting strong points of my teaching style. I have organized my evaluations below into two categories: those from students in courses I have taught, and those from peers and teaching professionals observing my lectures.
\subsection{Student Evaluations}
%Chart out survey responses for CO 327 with survey adjectives for context for scores (some here, rest in appendix)
%Student comment strong points
%Student comment targets for change
\subsection{Teaching Observations}\label{sec:teaching-observations}
One element of the CUT teaching program I took alongside my PhD was having lectures I give upervised by an expert in teaching working with the university's Centre for Teaching Excellence (CTE). I completed two teaching observations through the program. Below I summarize the feedback I received from these observations.
%highlights from 1st observation
\subsubsection*{First Teaching Observation}
\paragraph{}
My first observation was on the guest lecture I gave for Introduction to Game Theory in Fall $2018$ on Correlated Equilibria. The observation was conducted by Shahrukh Athar, a Graduate Instructional Developer working for the CTE. I have included the relevant sections of the full report in Appendix \ref{sec:observation-report-1}. The feedback in the report was divided in \emph{aspects to maintain}, where strengths of teaching were identified, and \emph{targets for change}, where opportunities for improvement were identified.
\paragraph{Aspects to Maintain} The first strength Shahrukh identified was my use of questions and comprehension checks. He appreciated the variety of checks I used, as well as the split between content-specific checks and general purpose open-ended questions. He commented that ``\emph{All of this is
fantastic as it demonstrates a learner-centric approach to teaching rather than a teacher-centric
one. It shows that you want to take your learners along with you as the lesson progresses and
are willing to pause and clarify confusions before moving on.}''

@@

When writing on the whiteboard, it is important not to talk as your back is turned to your audience. This creates a disconnect between the teacher and the learners. For example, a student may have their hand raised to signal to the instructor that they want to ask a question, but if the instructor is not looking towards the students then they can easily miss taking that question. This also leads to the loss of eye contact, which is an important aspect of interpersonal communication as it signals interest in others and helps in classroom management (such as preventing students from getting distracted from the material). I noted that you talked while writing on the board several times during the lesson. For example, when you were discussing different cases, you were almost continuously writing on the board and talking at the same time. In your future teaching opportunities, try to incorporate the Write-Turn-Talk technique, where you should write on the board first without talking, then turn towards the learners and talk while looking at them. Doing so will enable you to better engage the students into the learning process and will help you in keeping a bird’s eye view of the class.
\section{Teaching Observation Report 2}\label{sec:observation-report-2}
\emph{The teaching report presented below has been condensed from its original form in the interest of space.}

@@

\section{}
\end{document}

>>>>

\section{Evaluation of Teaching}
I find feedback on my teaching to be tremendously valuable. It is the easiest way for me to identify potential avenues for improvement, while at the same time motivating me by highlighting strong points of my teaching style. I have organized my evaluations below into two categories: those from students in courses I have taught, and those from peers and teaching professionals observing my lectures.
\subsection{Student Evaluations}
\subsubsection*{CO 327: Deterministic OR Models - Spring 2019}
\paragraph{}
At the end of the course students took a course exit survey evaluating the quality of my instruction and their impressions of the course. They were asked to rate aspects on the course on a scale of $1$ to $5$ where $1$ represents Very Poor, $2$ represents Unsatisfactory, $3$ represents Satisfactory, $4$ represents Good, and $5$ represents Excellent. The average scores appear in the charts below.
\begin{figure}[h]
\begin{tabular}{|r||c|c|c|c|}
     \hline
Aspect & Explanations & Questions & Visual Presentation & Oral Presentation\\
\hline
Average Score & $4.17$ & $4.57$ & $4.14$ & $4.29$ \\
\hline
\end{tabular}
\end{figure}
\begin{figure}[h]
\begin{tabular}{|r||c|c|c|c|}
     \hline
Aspect &  Organization & Availability & Ability to Hold Interest & Effectiveness  \\
\hline
Average Score & $3.86$ & $4.83$ & $3.43$ & $4.14$ \\
\hline
\end{tabular}
\end{figure}

My average score from these course evaluations is $4.17875$. To put this score in perspective, in an email communication with me the department head at the time commented ``$4.17875$ is a very good score. Your score is among the 2-3 best offerings out of the last 10! In particular, you beat several seasoned instructors with your performance.''

%Chart out survey responses for CO 327 with survey adjectives for context for scores (some here, rest in appendix)
%Student comment strong points
%Student comment targets for change
\subsection{Teaching Observations}\label{sec:teaching-observations}
One element of the CUT teaching program I took alongside my PhD was having lectures I give upervised by an expert in teaching working with the university's Centre for Teaching Excellence (CTE). I completed two teaching observations through the program. Below I summarize the feedback I received from these observations.
%highlights from 1st observation
\subsubsection*{First Teaching Observation}
\paragraph{}
My first observation was on the guest lecture I gave for Introduction to Game Theory in Fall $2018$ on Correlated Equilibria. The observation was conducted by Shahrukh Athar, a Graduate Instructional Developer working for the CTE. I have included the relevant sections of the full report in Appendix \ref{sec:observation-report-1}. The feedback in the report was divided in \emph{aspects to maintain}, where strengths of teaching were identified, and \emph{targets for change}, where opportunities for improvement were identified.
\paragraph{Aspects to Maintain} The first strength Shahrukh identified was my use of questions and comprehension checks. He appreciated the variety of checks I used, as well as the split between content-specific checks and general purpose open-ended questions. He commented that ``\emph{All of this is
fantastic as it demonstrates a learner-centric approach to teaching rather than a teacher-centric
one. It shows that you want to take your learners along with you as the lesson progresses and
are willing to pause and clarify confusions before moving on.}''

@@

When writing on the whiteboard, it is important not to talk as your back is turned to your audience. This creates a disconnect between the teacher and the learners. For example, a student may have their hand raised to signal to the instructor that they want to ask a question, but if the instructor is not looking towards the students then they can easily miss taking that question. This also leads to the loss of eye contact, which is an important aspect of interpersonal communication as it signals interest in others and helps in classroom management (such as preventing students from getting distracted from the material). I noted that you talked while writing on the board several times during the lesson. For example, when you were discussing different cases, you were almost continuously writing on the board and talking at the same time. In your future teaching opportunities, try to incorporate the Write-Turn-Talk technique, where you should write on the board first without talking, then turn towards the learners and talk while looking at them. Doing so will enable you to better engage the students into the learning process and will help you in keeping a bird’s eye view of the class.

\section{Teaching Observation Report 2}\label{sec:observation-report-2}
\emph{The teaching report presented below has been condensed from its original form in the interest of space.}

@@

\end{document}
